documentclass[a4paper,10pt]{article}
usepackage[utf8]{inputenc}
usepackage{geometry}
usepackage{hyperref}
usepackage{enumitem}
usepackage{parskip}
usepackage{xcolor}

geometry{top=1in, bottom=1in, left=1in, right=1in}

begin{document}

pagestyle{empty}
begin{center}
    \textbf{\Huge Ruqqiya Syed} \\
    Aerospace Engineer \\
    Lahore, Pakistan \\
    \href{tel:+923301629916}{03301629916} \quad | \quad \href{mailto:ruqqiya78@gmail.com}{ruqqiya78@gmail.com} \quad | \quad \href{https://www.linkedin.com/in/ruqqiya-syed}{LinkedIn}
end{center}

vspace{0.5cm}

noindent
textbf{\large Education} \\
textbf{Institute of Space Technology}, Islamabad \\
Bachelor of Science in Aerospace Engineering \hfill September 2020 – July 2024

vspace{0.5cm}

noindent
textbf{\large Experience} \\
textbf{Research and Development Division Intern} \\
textit{Pakistan Meteorological Department} \hfill Onsite \\
• Applied Python and Linux to automate climate data analysis and refine statistical models. \\
• Researched bias correction methods in statistical downscaling for hydrologic impact studies. \\
• Evaluated statistical models (Distribution Mapping, Linear Scaling, etc.) for improving accuracy metrics.

vspace{0.5cm}

noindent
textbf{Maintenance Trainee} \\
textit{Pakistan International Airlines} \hfill Onsite \\
• Gained knowledge of advanced cockpit systems, including the Engine Indication and Crew Alerting System (EICAS) for real-time monitoring. \\
• Contributed to tasks like Landing Gear overhaul, Oil Servicing, Filter change in the engine, and Engine washing in Base Maintenance. \\
• Learned navigation and control systems such as Primary Flight Displays (PFDs) and Control Display Units (CDUs).

vspace{0.5cm}

noindent
textbf{\large Projects}

noindent
textbf{3D Design of Aircraft using CAD} \hfill March 2021 – June 2021 \\
Designed a BOEING 747 aircraft using parameters based on researched blueprints, including airfoil tools for the wings, and assembled the parts using assembly design.

vspace{0.5cm}

noindent
textbf{Aircraft Performance Analysis} \hfill Nov. 2022 – Jan. 2023 \\
Calculated performance parameters of the Airbus A380-800 using MATLAB, researching data from various sources and the book \textit{Aircraft Vehicle Design and Performance}.

vspace{0.5cm}

noindent
textbf{Aircraft Vehicle Design} \hfill March 2023 – June 2023 \\
Worked on narrow-body aircraft design (Tupolev-TU114) using research from various papers and sources. Designed the aircraft in CATIA, RDS, and VSP after calculating parameters in MATLAB.

vspace{0.5cm}

noindent
textbf{The Meshing of Split Winglet} \hfill May 2023 – June 2023 \\
Meshed a split winglet in ANSYS Fluent, focusing on critical areas like the leading edge and junctions with inflation layers to ensure accurate aerodynamic simulation.

vspace{0.5cm}

noindent
textbf{Final Year Project} \hfill Sept. 2023 – July 2024 \\
Designed and analyzed the primary and secondary combustors of a solid propellant ramjet missile. Conducted thermochemical calculations and developed MATLAB algorithms to optimize the adiabatic flame temperature of the secondary combustor. Used CPROP PEP software to determine the enthalpy of formation for various reactions.

vspace{0.5cm}

noindent
textbf{\large Skills}

noindent
textbf{Technical:} CATIA, MATLAB, ANSYS, Python, Linux, MS Office, VSP, RDS \\
textbf{Analytical:} Data analysis, simulation modeling, and computational design

end{document}
